\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdftitle={Patrick David Elliott's CV},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother


\title{Patrick David Elliott's CV}
\date{}

\begin{document}
\maketitle

(last updated 30.10.2016; available as a pdf here.)

\subsection{Contact}\label{contact}

\href{mailto:p.elliott@ucl.ac.uk}{\nolinkurl{p.elliott@ucl.ac.uk}}\\
Chandler House\\
2 Wakefield Street\\
London WC1N 1PF\\
(+44)7833896276

\subsection{Research Themes}\label{research-themes}

\begin{itemize}
\item
  Broad interests: linguistic theory, syntax, semantics, the interfaces,
  pragmatics, philosophy of language
\item
  Specific interests:

  \begin{itemize}
  \tightlist
  \item
    Division of labour between syntax and semantics in linguistic theory
    generally.
  \item
    Syntax and semantics of clausal embedding.
  \item
    Syntactic and semantic constraints on scope-taking.
  \item
    Conditions under which linguistic material can go missing
    (``ellipsis'').
  \item
    The interpretation of questions.
  \end{itemize}
\item
  Collaborators:
  \href{https://www.ucl.ac.uk/pals/people/profiles/academic-staff/klaus-abels}{Klaus
  Abels (University College London)},
  \href{http://ling.yale.edu/people/matt-barros}{Matt Barros (Yale
  University)},
  \href{https://www.ucl.ac.uk/pals/people/profiles/academic-stbineraff/nathan-klinedinst}{Nathan
  Klinedinst (University College London)},
  \href{https://sites.google.com/site/esmccready/}{Eric McCready (Aoyama
  Gakuin University)}, \href{home.uni-leipzig.de/murphy/}{Andrew Murphy
  (Universität Leipzig)},
  \href{https://sites.google.com/site/andreeanicolae/}{Andreea Nicolae
  (Zentrum für Allgemeine Sprachwissenschaft)},
  \href{www.ucl.ac.uk/~ucjtudo/}{Yasutada Sudo (University College
  London)}, \href{https://sites.google.com/site/garythoms/}{Gary Thoms
  (University of Glasgow)},
  \href{https://sites.google.com/site/esmccready/}{Wataru Uegaki (Leiden
  University)},
  \href{https://www.hud.ac.uk/ourstaff/profile/index.php?staffid=1451}{Rebecca
  Woods (University of Huddersfield)} 
\end{itemize}

\subsection{Education}\label{education}

\subsubsection{September 2013 -}\label{september-2013--}

University College London, London, United Kingdom\\
PhD in Linguistics, September 2017 (expected)\\
Thesis: embedding meanings and structures (title TBC)\\
Advisors:
\href{https://www.ucl.ac.uk/pals/people/profiles/academic-staff/klaus-abels}{Dr.~Klaus
Abels} (primary) and \href{https://www.ucl.ac.uk/~ucjtudo/}{Dr.~Yasutada
Sudo} (secondary)\\
Funding body: \href{http://www.ahrc.ac.uk/}{The Arts and Humanities
Research Council}

\subsubsection{October 2016 - January
2017}\label{october-2016---january-2017}

Zentrum für Allgemeine Sprachwissenschaft, Berlin, Germany\\
Position: Visiting Scholar\\
Mentor:
\href{http://www.zas.gwz-berlin.de/mitarbeiter_sauerland.html}{Dr.~Uli
Sauerland}\\
Funding body: \href{https://www.erasmusplus.org.uk/}{Erasmus+}

\subsubsection{July - August 2016}\label{july---august-2016}

North American Summer School on Language, Logic and Information\\
Rutgers, United States

\subsubsection{September 2012 - September
2013}\label{september-2012---september-2013}

University of Edinburgh, Edinburgh, United Kingdom\\
MSc by Research in Theoretical Linguistics\\
Thesis: \emph{Clausal Ellipsis and Identity}\\
Advisors: \href{http://www.lel.ed.ac.uk/~packema/}{Dr.~Peter Ackema}
(primary) and \href{https://sites.google.com/site/garythoms/}{Dr.~Gary
Thoms} (secondary)\\
Class: distinction

\subsubsection{September 2008 - September
2012}\label{september-2008---september-2012}

University College London, London, United Kingdom\\
BA in Linguistics (International Programme)\\
Thesis: \emph{The Distribution and Interpretation of the German Simplex
Anaphor}\\
Advisor:
\href{https://www.ucl.ac.uk/pals/people/profiles/academic-staff/hans-van-de-koot}{Dr.~Hans
van de Koot}\\
Class: 1st (thesis and all modules)

\subsubsection{September 2010 - September
2011}\label{september-2010---september-2011}

Eberhard Karls Universität Tübingen, Tübingen, Germany\\
Position: Erasmus visiting student\\
Project: \emph{Modelling Implicature}\\
Advisor: \href{http://www.sfs.uni-tubeingen.de/~roland/}{Dr.~Roland
Mühlenbernd}

\subsection{Awards and Honours}\label{awards-and-honours}

\begin{itemize}
\tightlist
\item
  2016

  \begin{itemize}
  \tightlist
  \item
    Conference Travel Grant\\
    Awarding body: The Philological Society\\
    \emph{To present at the 52nd Annual Meeting of the Chicago
    Linguistics Society, Chicago.}
  \end{itemize}
\item
  2015

  \begin{itemize}
  \tightlist
  \item
    Student bursary\\
    Awarding body: Generative Linguistics in the Old World
  \item
    Conference Travel Grant\\
    Awarding body: University College London\\
    \emph{To present at the 33rd West Coast Conference on Formal
    Linguistics, Simon Fraser University, Vancouver.}
  \end{itemize}
\item
  2014

  \begin{itemize}
  \tightlist
  \item
    Student bursary\\
    Awarding body: Linguistics Association of Great Britain
  \item
    Conference Travel Grant\\
    Awarding body: Department of Linguistics, University College
    London\\
    \emph{To present at Semantics And Linguistic Theory 24, New York
    University, New York.}
  \end{itemize}
\item
  2013

  \begin{itemize}
  \tightlist
  \item
    Doctoral studentship\\
    Awarding body: Arts and Humantities Research Council
  \item
    Conference Travel Grant\\
    Awarding body: Linguistics and English Language, University of
    Edinburgh\\
    \emph{To present at the 49th Annual Meeting of the Chicago
    Linguistics Society, Chicago.}
  \end{itemize}
\item
  2012

  \begin{itemize}
  \tightlist
  \item
    Faculty of Brain Sciences Prize\\
    Awarding body: Faculty of Brain Sciences, University College
    London.\\
    \emph{For outstanding academic performance over the course of an
    undergraduate degree in the faculty of Brain Sciences.}
  \end{itemize}
\item
  2010

  \begin{itemize}
  \tightlist
  \item
    Alexander Melville Bell Prize\\
    Awarding body: Department of Linguistics, University College
    London.\\
    \emph{For exemplary academic performance September 2009 - September
    2010.}
  \end{itemize}
\item
  2009

  \begin{itemize}
  \tightlist
  \item
    Commendation from the BA Linguistics Examination Board\\
    Awarding body: Department of Linguistics, University College London.
  \item
    Alexander Melville Bell Prize\\
    Awarding body: Department of Linguistics, University College
    London.\\
    \emph{For exemplary academic performance September 2008 - September
    2009.}
  \end{itemize}
\end{itemize}

\subsection{Publications}\label{publications}

\subsubsection{Journal articles}\label{journal-articles}

\begin{itemize}
\tightlist
\item
  Under revision

  \begin{itemize}
  \tightlist
  \item
    ``There is no island repair''\\
    with \href{...}{Matt Barros} and \href{...}{Gary Thoms}\\
    Draft on \href{http://ling.auf.net/lingbuzz/002100}{LingBuzz}
  \item
    ``Predicates of relevance and theories of question embedding''\\
    with \href{...}{Nathan Klinedinst}, \href{...}{Yasutada Sudo}, and
    \href{...}{Wataru Uegaki}
  \end{itemize}
\item
  Under review

  \begin{itemize}
  \tightlist
  \item
    ``Do superiority-violating multiple questions have pair-list
    readings?'' with \href{...}{Andreea Nicolae} and \href{...}{Yasutada
    Sudo}
  \end{itemize}
\item
  2015

  \begin{itemize}
  \tightlist
  \item
    ``Pair-list readings of conjoined singular \emph{which}-phrases''\\
    with \href{...}{Andreea Nicolae} and \href{...}{Yasutada Sudo}
  \end{itemize}
\item
  In prep.

  \begin{itemize}
  \tightlist
  \item
    ``Nested \emph{wh}-questions and the locality of scope taking''
  \item
    ``Remarks on superiority and economy''\\
    with \href{...}{Klaus Abels}
  \end{itemize}
\item
  Unpublished manuscripts
\item
  ``Sorting out multiple questions''\\
  Upgrade paper, University College London
\end{itemize}

\subsubsection{Proceedings papers}\label{proceedings-papers}

\begin{itemize}
\tightlist
\item
  In prep

  \begin{itemize}
  \tightlist
  \item
    ``Embedded declaratives as modifiers'' Proceedings of Sinn und
    Bedeutung 21
  \item
    ``Nested \emph{wh}-questions and the locality of scope taking''\\
    Proceedings of ConSOLE XXIV
  \end{itemize}
\item
  To appear

  \begin{itemize}
  \tightlist
  \item
    ``Explaing DPs vs CPs without syntax''\\
    Proceedings of the 52nd annual meeting of the Chicago Linguistics
    Society\\
    Draft on \href{http://ling.auf.net/lingbuzz/003128}{LingBuzz} and
    \href{http://www.semanticsarchive.net/Archive/zY4NGRlY/}{Semantics
    Archive}
  \item
    ``List readings of conjoined singular \emph{which}-phrases''\\
    with \href{...}{Andreea Nicolae} and \href{...}{Yasutada Sudo}\\
    Proceedings of NELS 46
  \end{itemize}
\item
  2016

  \begin{itemize}
  \tightlist
  \item
    ``E-type readings of quantifiers under ellipsis''\\
    with \href{...}{Yasutada Sudo}\\
    Proceedings of Sinn und Bedeutung 20
  \item
    ``QR out of control''\\
    with \href{...}{Gary Thoms} Proceedings of WCCFL 33
  \end{itemize}
\item
  2015

  \begin{itemize}
  \tightlist
  \item
    ``More variation in island repair: the clausal/non-clausal
    distinction''\\
    with \href{...}{Matt Barros} and \href{...}{Gary Thoms}\\
    Proceedings of CLS 49
  \end{itemize}
\end{itemize}

\subsection{Presentations}\label{presentations}

\subsubsection{Refereed conference
presentations}\label{refereed-conference-presentations}

\begin{itemize}
\tightlist
\item
  2017

  \begin{itemize}
  \tightlist
  \item
    ``Who and what do \emph{who} and \emph{what} range over
    cross-linguistically?'' with
    \href{https://sites.google.com/site/andreeanicolae/}{Andreea
    Nicolae} and
    \href{http://www.zas.gwz-berlin.de/mitarbeiter_sauerland.html}{Uli
    Sauerland}.\\
    Theoretical and Experimental Approaches to Presuppositions, Genoa,
    Italy, 3-5 March, 2017.
  \item
    ``Cumulative readings beyond nominals'' with
    \href{https://sites.google.com/site/andreeanicolae/}{Andreea
    Nicolae}.\\
    Poster at the LSA 2017 Annual Meeting, Austin, Texas, 5-8 January,
    2017.
  \item
    ``Superiority, economy, and information structure''\\
    ConSOLE XXV, University of Leipzig, 4-7 January, 2017.
  \end{itemize}
\item
  2016

  \begin{itemize}
  \tightlist
  \item
    ``Predicates of relevance and theories of question embedding''\\
    with
    \href{https://www.ucl.ac.uk/pals/people/profiles/academic-staff/nathan-klinedinst}{Nathan
    Klinedinst}, \href{http://www.ucl.ac.uk/~ucjtudo/}{Yasutada Sudo},
    and \href{https://wataruu.wordpress.com}{Wataru Uegaki}.\\
    \href{http://umass2016.nelsconference.org/}{North East Linguistics
    Society (NELS) 47}, University of Massachusetts Amherst, October
    14-16, 2016.
  \item
    ``NPI anti-licensing in peripheral modifiers''\\
    with \href{https://sites.google.com/site/garythoms/}{Gary Thoms}.\\
    \href{http://www.lagb.org.uk/lagb2016/home}{2016 Annual Meeting of
    the Linguistics Association of Great Britain (LAGB)}, University of
    York, 6-9 September, 2016.
  \item
    ``Cumulative readings beyond nominals''\\
    with \href{https://sites.google.com/site/andreeanicolae/}{Andreea
    Nicolae}.\\
    \href{http://www.lagb.org.uk/lagb2016/home}{2016 Annual Meeting of
    the Linguistics Association of Great Britain (LAGB)}, University of
    York, 6-9 September, 2016.
  \item
    ``Embedded declaratives as modifiers''\\
    Sinn und Bedeutung 21, University of Edinburgh, 4-6 September, 2016.
  \item
    ``Propositional content of events and individuals''\\
    Poster at the North American Summer School on Language, Logic, and
    Information (NASSLLI) Student Session, Rutgers University, 9-16
    July, 2016.
  \item
    ``Selection without syntax: explaining the difference between
    clauses and nominal phrases''\\
    Poster at \href{http://olinco.upol.cz/}{the 2016 Olomouc Linguistics
    Colloquium (Olinco)}, 9-11 June, 2016.
  \item
    ``Non-intersective readings in the Slavic Noun Phrase: diagnosing
    two varieties of left branch extraction''\\
    with \href{http://home.uni-leipzig.de/murphy/}{Andrew Murphy}\\
    Poster at \href{http://olinco.upol.cz/}{the 2016 Olomouc Linguistics
    Colloquium (Olinco)}, 9-11 June, 2016.
  \item
    ``Explaining DPs vs.~CPs without syntax''\\
    \href{http://chicagolinguisticsociety.org/}{52nd Annual Meeting of
    the Chicago Linguistics Society (CLS 52)}, University of Chicago,
    21-23 April, 2016.
  \item
    ``Nested \emph{which}-phrases: consequences for the syntax of
    wh-scope''\\
    \href{http://www.cril.unisalento.it/igg2016/}{Incontro di Grammatica
    Generativa 42}, University of Salento, 18-20 February, 2016.
  \item
    ``Nested \emph{wh}-questions and the locality of scope taking''\\
    \href{https://sites.google.com/a/york.ac.uk/consolexxiv/home}{24th
    Conference of the Student Organisation of Linguistics in Europe
    (ConSOLE XXIV)}, 6-8 January, 2016.
  \end{itemize}
\item
  2015

  \begin{itemize}
  \tightlist
  \item
    ``Pair-list readings of conjoined singular \emph{which}-phrases''\\
    with \href{..}{Andreea Nicolae} and \href{...}{Yasutada Sudo}\\
    \href{http://linguistics.concordia.ca/nels46/}{North East
    Linguistics Society (NELS) 46}, Concordia University, 16-18 October,
    2016.
  \item
    ``E-type readings of quantifiers under ellipsis: consequences for
    the identity condition''\\
    with \href{http://www.ucl.ac.uk/~ucjtudo/}{Yasutada Sudo}\\
    Poster at
    \href{https://sites.google.com/site/sinnundbedeutung20/home}{Sinn
    und Bedeutung 20}, Universität Tübingen, 9-12 September, 2016.
  \item
    ``Discourse \emph{even} vs.~attitude \emph{even}''\\
    with \href{http://www.ucl.ac.uk/~ucjtudo/}{Yasutada Sudo} and Eric
    McCready\\
    Poster at \href{...}{Semantics And Linguistic Theory (SALT) 25},
    Stanford University,
  \item
    ``Optimizing the Ellipsis Site''\\
    with \href{...}{Andrew Murphy}\\
    \href{http://www.iel.unicamp.br/ellipsis/}{Grasping Ellipsis: its
    syntax, semantics, acquisition and processing}, University of
    Campinas, 4-5 May, 2015.
  \item
    ``Forming chains with covert copies: deriving the locality
    constraints on QR''\\
    with \href{...}{Gary Thoms} Poster at
    \href{https://sites.google.com/site/2015glow/home}{Generative
    Linguistics in the Old World (GLOW) 38}, Paris, 15-18 April, 2015.
  \item
    ``QR out of Control''\\
    with \href{...}{Gary Thoms}\\
    \href{https://sites.google.com/site/wccflsfu/}{West Coast Conference
    on Formal Linguistics (WCCFL) 33}, 27-29 March, 2015.
  \end{itemize}
\item
  2014

  \begin{itemize}
  \tightlist
  \item
    ``E-type readings of quantifiers Under ellipsis''\\
    with \href{http://www.ucl.ac.uk/~ucjtudo/}{Yasutada Sudo}\\
    \href{http://www.lagb.org.uk/lagb2014/home}{2014 Annual Meeting of
    the Linguistics Association of Great Britain (LAGB)}, 1-5 September,
    2014.
  \item
    ``VP ellipsis without parallel binding: towards a QUD approach''\\
    with \href{...}{Andreea Nicolae} and
    \href{http://www.ucl.ac.uk/~ucjtudo/}{Yasutada Sudo}
  \item
    ``Ellipsis identity and structural economy''\\
    9th Newcastle upon Tyne Postgraduate Conference in Linguistics, 4
    April, 2014.
  \end{itemize}
\item
  2013

  \begin{itemize}
  \tightlist
  \item
    ``Towards a dual account of ellipsis identity''\\
    \href{https://mfilconf.wordpress.com/archive/mfil-2013-programme/}{2013
    Manchester Forum in Linguistics}, University of Manchester, 15-16
    November 2016.
  \item
    ``Island evasion explains variability in island repair''\\
    \href{https://mfilconf.wordpress.com/archive/mfil-2013-programme/}{2013
    Manchester Forum in Linguistics}, University of Manchester, 15-16
    November 2016.
  \item
    ``Towards a theory of radical island evasion under ellipsis''\\
    Linguistics and English Language Postgraduate Conference, University
    of Edinburgh, 22 May 2013.
  \item
    ``No sluice is an island''\\
    Poster at the Postgraduate Linguistics Workshop, University of
    St.~Andrews, 25 March 2013.
  \item
    ``More variation in island repair: The clausal/non-clausal
    distinction''\\
    with \href{...}{Matt Barros} and \href{...}{Gary Thoms}\\
    \href{...}{The 49th Annual Meeting of the Chicago Linguistics
    Society (CLS)}, 19 April 2013.
  \end{itemize}
\end{itemize}

\subsubsection{Invited presentations}\label{invited-presentations}

\begin{itemize}
\tightlist
\item
  2016

  \begin{itemize}
  \tightlist
  \item
    ``Ellipsis identity and the alternative tier''\\
    Theory of the Grammar colloquium, Universität Leipzig, 11 November,
    2016.
  \item
    ``Severing everything: substitution failures and their consequences
    for the theory of argument structure''\\
    Roundtable, UCLA, 25 April 2016.
  \end{itemize}
\item
  2015

  \begin{itemize}
  \tightlist
  \item
    ``Nested \emph{wh}-questions and the locality of scope-taking''\\
    Questions at the Syntax-Semantics Interface workshop, University
    College London, September 2015.
  \item
    ``Remarks on the Coordination of DPs and CPs''\\
    with \href{...}{Luke Burke}\\
    Interactions between Syntax and Semantics Across Frameworks
    workshop, University of Cambridge, 8 January 2015.
  \end{itemize}
\item
  2014

  \begin{itemize}
  \tightlist
  \item
    ``Illusory repair and the PF Theory of Islands''\\
    LF Reading Group, Massachusetts Institute of Technology, June 2014.
  \end{itemize}
\item
  2013

  \begin{itemize}
  \tightlist
  \item
    ``Island evasion explains variability in island repair''\\
    with \href{...}{Matt Barros} and \href{...}{Gary Thoms}\\
    Edinburgh Ellipsis Workshop, University of Edinburgh, 29 May 2013.
  \end{itemize}
\item
  2012

  \begin{itemize}
  \tightlist
  \item
    ``Illusory island repair in sluicing: Evidence from non-predicative
    adjectives''\\
    Syntax and Semantics Reading Group, University of Edinburgh, 10
    October 2012.
  \end{itemize}
\end{itemize}

\subsubsection{Other}\label{other}

\begin{itemize}
\tightlist
\item
  2016

  \begin{itemize}
  \tightlist
  \item
    ``\emph{That}-clauses as event modifiers''\\
    PhD Day, University College London, 24 May 2016.
  \item
    ``\emph{Explain} and the semantics of embedding''\\
    London Semantics Day, Queen Mary University of London, 10 May, 2016.
  \end{itemize}
\item
  2015

  \begin{itemize}
  \tightlist
  \item
    ``Questions and correlatives: a common semantic core''\\
    with
    \href{http://linguistics.sllf.qmul.ac.uk/people/anne-beshears}{Anne
    Beshears}\\
    \href{...}{Eastern Generative Grammar (EGG) open podium}, Brno,
    August 2015.
  \item
    ``On the ambiguity of multiple questions''\\
    PhD Day, University College London, June 2015.
  \item
    ``Sorting out multiple questions''\\
    London Semantics Day, Queen Mary University of London, May 2015.
  \end{itemize}
\item
  2014

  \begin{itemize}
  \tightlist
  \item
    ``VP ellipsis without parallel binding: Towards a QUD approach''\\
    with \href{...}{Andreea Nicolae} and \href{...}{Yasutada Sudo}\\
    University College London.
  \end{itemize}
\end{itemize}

\subsection{Teaching}\label{teaching}

\begin{itemize}
\tightlist
\item
  Spring 2016

  \begin{itemize}
  \tightlist
  \item
    Guest lecturer for PLING228: Semantics Research Seminar\\
    Course conveners: Dr.~Nathan Klinedinst, Dr.~Daniel Rothschild, and
    Dr.~Yasutada Sudo.\\
    Two classes on the semantics of questions and plurality
  \item
    Teaching assistant for PLIN2203/PLING226: Intermediate Generative
    Grammar B\\
    Lecturer: Sam Steddy
  \item
    Teaching assistant
  \end{itemize}
\end{itemize}

\begin{itemize}
\tightlist
\item
  Spring 2015

  \begin{itemize}
  \tightlist
  \item
    Teaching assistant for PLIN1202: Introduction to Generative Grammar
    B\\
    Lecturer: Dr.~Hans van de Koot
  \item
    Teaching assistant for PLIN1302: Introduction to Language\\
    Lecturer: Prof.~Andrew Nevins
  \item
    Teaching assistant for Introduction to Semantics and Pragmatics B\\
    Lecturer: Dr.~Nathan Klinedinst
  \end{itemize}
\item
  Fall 2014

  \begin{itemize}
  \tightlist
  \item
    Teaching assistant for \href{http://www.actl.ucl.ac.uk/}{Advanced
    Core Training in Linguistics}: syntax strand\\
    Lecturer: Dr.~Klaus Abels
  \item
    Teaching assistant for PLIN1201: Introduction to Generative Grammar
    A\\
    Lecturer: Dr.~Klaus Abels
  \end{itemize}
\item
  Spring 2014

  \begin{itemize}
  \tightlist
  \item
    Teaching assistant for Introduction to Semantics and Pragmatics B\\
    Lecturer: Dr.~Nathan Klinedinst
  \item
    Teaching assistant for PLIN1302: Introduction to Language\\
    Lecturer: Ezekiel Panitz
  \end{itemize}
\end{itemize}

\subsection{Professional service}\label{professional-service}

\begin{itemize}
\tightlist
\item
  Professional bodies

  \begin{itemize}
  \tightlist
  \item
    Chair of the Linguistics Association of Great Britain Student
    Committee from 2016 to present.
  \item
    Member of the Linguistics Association of Great Britain Student
    Committee from 2014 to present.
  \item
    Member of the Philological Society
  \end{itemize}
\item
  Editorial work

  \begin{itemize}
  \tightlist
  \item
    Editorial assistant for Linguistic Inquiry Squibs and Discussion
    section (paid): BLANK
  \item
    Editor (joint with Ezekiel Panitz) of the University College London
    Working Papers in Linguistics.
  \end{itemize}
\item
  Paper reviewing

  \begin{itemize}
  \tightlist
  \item
    Linguistics in the Netherlands
  \item
    Lingua
  \item
    Journal of Pragmatics
  \end{itemize}
\item
  Abstract reviewing

  \begin{itemize}
  \tightlist
  \item
    25th Conference of the Student Organisation of Linguistics in Europe
    (ConSOLE 25): 2016
  \item
    47th Annual Meeting of the North East Linguistics Society (NELS 47):
    2016
  \item
    Linguistics Association of Great Britain annual meeting: 2016, 2015
  \item
    Sinn und Bedeutung (SuB) 21: 2016
  \item
    Ellipsis Across Borders Conference (eab2016sa): 2016
  \item
    Student Session of the 28th European Summer School in Logic,
    Language and Information (ESSLLI StuS 2016): 2016
  \item
    24th Conference of the Student Organisation of Linguistics in Europe
    (ConSOLE 24): 2015
  \item
    University College London Postgraduate Conference in Linguistics
  \end{itemize}
\item
  Organization

  \begin{itemize}
  \tightlist
  \item
    Organizer (joint with Elliot Murphy and Caterina Paolazzi) of the
    University College London Syntax Reading Group: 2015-present.
  \item
    Organizer (joint with Luke Burke) of the London Linguistics and
    Philosophy Seminar Series: 2014-2015
  \item
    Organizer (joint with Jessica Brown, Luke Burke, and Tom Stanton) of
    the Grammatical Formalisms Reading Group: October-December 2014
  \item
    Organizer (joint with Luke Burke) of the London Linguistics and
    Philosophy Reading Group: 2013-2014
  \item
    Organizer (joint with Ezekiel Panitz) of the workshop
    \emph{Questions at the Syntax Semantics Interface}, University
    College London.
  \item
    Organizer (joint with Luke Burke, Jessica Brown, and Tom Stanton) of
    the workshop \emph{Interactions between Syntax and Semantics Across
    Frameworks}, University of Cambridge
  \end{itemize}
\end{itemize}

\subsection{Languages}\label{languages}

\begin{itemize}
\tightlist
\item
  English (native), German (advanced)
\end{itemize}

\subsection{Technology experience}\label{technology-experience}

\begin{itemize}
\tightlist
\item
  Languages: TeX, haskell, web (html, css, and javascript), nix, and
  shell script.
\item
  Extensive experience with linux/unix and GNU core utils.
\end{itemize}

\subsection{References}\label{references}

\begin{itemize}
\tightlist
\item
  Dr.~Klaus Abels

  \begin{itemize}
  \tightlist
  \item
    Reading in Linguistics, University College London\\
    115b, 2 Wakefield Street\\
    Chandler House\\
    London, WC1N 1PF\\
    +442076794061
  \end{itemize}
\item
  Dr.~Uli Sauerland

  \begin{itemize}
  \tightlist
  \item
    Programmbereichskoordinator, Zentrum für Allgemeine
    Sprachwissenschaft\\
    Schützenstr. 18\\
    D-10117 Berlin\\
    +493020192570
  \end{itemize}
\end{itemize}

\end{document}
